Forecasting Gamma-ray Bursts using Gravitational Waves

### 2018-02-26 Paper/Manuscript.tex
Added a few more lines

We will set $a=0.9$ cite, $M_\text{BH} =5 M_\odot$ cite(Morgan's email), $R_\text{NS} = 12\,$km

>>>>

We will set $M_\text{BH} =5 M_\odot$ cite(Morgan's email) $a=0.9$ cite,, $R_\text{NS} = 12\,$km
For inspiral timescales it doesn't actually matter where the ISCO is as the time difference between a plunge at 6M vs. one at M is (compute).
What matter is mass of the black hole, we will simply make the assmpution that there exist black holes with high spins at that mass scale.
